market-justice-preferences

### 2024-06-25 05-discussion.qmd
Update varios y render

$H_7$ Falta solo esto

>>>>

Hypothesis $H7$ posited that the academic performance of schools could moderate the effect of meritocratic perceptions on preferences for market justice. This hypothesis is based on the argument that the level of academic performance in schools entails a differentiated promotion of meritocratic perceptions to achieve better results, which would, in turn, reinforce or diminish preferences for market justice. The results of the interactions between levels suggest that, indeed, in higher-performing schools, the effect of meritocratic perceptions on the justification of service provision based on market principles is weaker compared to lower-performing schools. Similarly to the effect of academic performance in $H4$, a possible explanation for this moderation is that students in high-performing schools may be more exposed to knowledge about the effects of inequality and social justice. This exposure translates into an enlightening effect of education on inequality, which can mitigate the impact of meritocracy on market justice preferences.
